Estimations plots

### 2024-02-01 procesamiento/prod_analysis-plots-models.Rmd
ajustes color plots

df_pred1 <- plot_predictions(int_homo, condition = c("homclass","class3"),draw = F) 
# names(df_pred1)
df_pred1 %>% 
ggplot(aes(y =estimate,x=homclass, fill=class3, color=class3,ymin=conf.low, ymax=conf.high)) +
  geom_line(size=0.75) +
  geom_point(size=1) +
  geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
  facet_grid(~factor(class3, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class (VI+VII)","Intermediate class (III+IV+V)","Service Class (I+II)"))) +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  xlab("Network homogeneity (Full ties)")+
  ylab("Redistributive preferences") +
  theme(legend.position = "none", legend.title = element_blank())

>>>>

df_pred1 <- plot_predictions(int_homo, condition = c("homclass","class3"),draw = F) 
# names(df_pred1)
df_pred1 %>% 
ggplot(aes(y =estimate,x=homclass, fill=class3, color=class3,ymin=conf.low, ymax=conf.high)) +
  geom_line(size=0.75) +
  geom_point(size=1) +
  geom_ribbon(alpha=0.2,size=0.5,linetype=1) +
  facet_grid(~factor(class3, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class (VI+VII)","Intermediate class (III+IV+V)","Service Class (I+II)"))) +
    scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
  scale_color_manual(values=c("#377EB8","#4DAF4A","#E41A1C"))+
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  xlab("Network homogeneity (Full ties)")+
  ylab("Redistributive preferences") +
  theme(legend.position = "none", legend.title = element_blank())
